Data Parallel Training of Neural Networks

### 2019-07-31 paper/paper.tex
ADD: appendix with additonal figures

\appendix[Additional Experimental Results]

\begin{figure}[!t]
\centering
\includegraphics[width=2.5in]{../evaluation/diagrams-paper/validation-loss-by-time-and-bs--MNIST}
\caption{The validation loss by training time for different batch sizes using sequential training, LeNet5 and MNIST.
This figure is related to \autoref{fig:loss_by_epoch} to the extent that the same data is displayed -- once per epoch and once per training time.
Displaying the loss by time demonstrates how larger batch sizes result in faster epochs but selecting too large batch sizes can compromise the convergence.}
\label{fig:loss_by_time}
\end{figure}

>>>>

\vfill\null
\newpage

\appendix[Additional Experimental Results]
We also evaluated our implementation using the TorchNet model and CIFAR10 dataset.
Since those results regarding parallelism are fairly similar to training LeNet5 on MNSIT, they are displayed in this appendix.

\autoref{fig:validation_loss_model_dataset} gives the validation loss per epoch for LeNet5 and TorchNet on both MNIST and CIFAR10.
We observe that MNIST requires fewer epochs than CIFAR10 to converge and reaches a better overall accuracy even after training for five times as many epochs.
No significant difference between the two models, LeNet5 and TorchNet, is visible.
Since they a fairly similar architecture, this is somewhat expected.

\begin{figure}[ht]
\centering
\includegraphics[width=2.5in]{../evaluation/diagrams-paper/validation-loss-by-model-and-dataset--bs-256}
\caption{The sequential validation loss per epoch when training the CNNs LeNet5 and TorchNet on the datasets MNIST and CIFAR10.
Training on MNIST requires significantly fewer epochs than CIFAR10 while also achieving higher overall accuracy.
There is no drastic difference between the two models.
In general, LeNet5 performs slightly better in the first few epochs, but TorchNet achieves higher final accuracy.}
\label{fig:validation_loss_model_dataset}
\end{figure}

The speedup per epoch is given in \autoref{fig:speedup_model_dataset}.
All four tested model-dataset combination scale similarly well.
The observations made in \autoref{sec:experimental_results} for LeNet5 and MNIST are therefore also applicable to TorchNet and CIFAR10.

\begin{figure}[ht]
\centering
\includegraphics[width=2.5in]{../evaluation/diagrams-paper/speedup-all--bs-256}
\caption{The speedup and efficiency per epoch on the GPU using all combinations of the two models and datasets with batch size 256.
All four variants demonstrate very similar parallel behavior.}
\label{fig:speedup_model_dataset}
\end{figure}
